\begin{thebibliography}{9}
\bibitem{robocup}
	Oficjalna strona Ligi \textit{RoboCup} dostępna pod adresem:\\
	\url{www.robocup.org}
	
\bibitem{RRT}
J. Bruce, M. Veloso:
\emph{Real-Time Randomized Path Planning for Robot Navigation}. Carnegie Mellon University

\bibitem{duleba}
	I. Dulęba:
	\emph{Metody i algorytmy planowania ruchu robotów mobilnych i manipulacyjnych}.
	Warszawa, Akademicka Oficyna Wydawnicza EXIT, 2001.

\bibitem{CVM_1}
	T. Quasn, L.Pyeatt, J.Moore:
	\emph{Curvature-Velocity Method for Differentially Steered Robots}.
	AI Robotics Lab
	Computer Science Department,
	Texas Tech University, 2003.

\bibitem{CVM_2}
	R. Simmons:
	\emph{The Curvature-Velocity Method for Local Obstacle Avoidance}.
	School of Computer Science,
	Carnegie Mellon University, 1996.
\bibitem{majchrowski}
	M. Majchrowski:
	\emph{Algorytm unikania kolizji przez robota mobilnego bazujący na przeszukiwaniu
	przestrzeni prędkości}.
	Praca Magisterska, Politechnika Warszawska, 2006.

\bibitem{VFH_1}
	J. Borenstein, Y. Koren:
	\emph{ The vector field histogram -- fast obstacle avoidance for mobile robots}.
	IEEE Transaction on Robotics and Automation, 1991.

\bibitem{VFH_2}
	J. Borenstein,Y. Koren:
	\emph{Histogramic in-motion mapping
	for mobile robot obstacle avoidance}.
	Department of Mechanical Engineering and Applied Mechanics,
	The University of Michigan, 1991.

\bibitem{dynamic_window}
	D. Fox, W. Burgard, S. Thrun:
	\emph{The Dynamic Window Approach to Collision Avoidance}.
	Department of Computer Science, University of Bonn;
	Department of Computer Science, Carnegie Mellon University, Pittsburgh, 1991.
		
 \bibitem{stp}
	B.Browning, J.Bruce, M.Bowling, M.Veloso:
	\emph{STP: Skills, tactics and plays for multi-robot control
             in adversarial environments.}
	  Carnegie Mellon University, 2004.
	  
\end{thebibliography}
